
\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}

\title{NB/BD Program toward RH: Version 5 (Proof Roadmap)}
\author{세라비 \& 세라피}
\date{}

\begin{document}
\maketitle

\section{Introduction}
Version 4 demonstrated numerically the simultaneous satisfaction of two core conditions:
(i) $M<0$ (negative main--diag) and 
(ii) off--diag suppression at the $1/\log N$ scale.
Version 5 outlines the steps needed to convert this into a rigorous proof.

\section{Correct Frame Alignment}
We must work within the exact Nyman--Beurling/Báez-Duarte (NB/BD) frame:
\begin{itemize}
\item Admissible functions $f(t)$ with weight $w(t)=1/(1/4+t^2)$.
\item Approximation of $1$ in $L^2(w)$ by linear combinations of $n^{it-1}$.
\end{itemize}
Any modified kernel or basis (e.g. band-limited, phase-modulated Gaussians) must be shown equivalent to legal test functions under this frame.

\section{Uniform Bounds}
Prove that for sufficiently large $N$,
\begin{equation}
M(c^\*) \le -\theta \sum|a_n|^2, 
\quad 
\frac{E_{\mathrm{off}}(c^\*)}{\sum|a_n|^2} \le \frac{C}{\log N},
\end{equation}
with constants $\theta, C > 0$ independent of $N$.

\section{Regularity of Basis}
Check that chosen modes (Gaussian, phase-modulated, $\mu(n)/n$) belong to admissible closure. 
Demonstrate $L^2$ integrability and bounded growth.

\section{Residual Terms}
Control truncation and discretization errors explicitly. 
Bound remainder $R_T$ for truncation $T=N^\gamma$.

\section{Closing the Chain}
Combine estimates to show
\begin{equation}
d_N^2 \le -\theta \sum|a_n|^2 + \frac{C}{\log N}\sum|a_n|^2 + o(1).
\end{equation}
For large $N$, $\frac{C}{\log N} < \theta$ holds, hence $d_N \to 0$, equivalent to RH.

\section{Conclusion}
Version 5 establishes a roadmap: aligning with NB/BD rigor, proving uniform bounds, and controlling residuals. 
This sets the stage for transforming numerical evidence (V4) into a proof strategy.

\end{document}
