
\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}

\title{NB/BD Program toward RH: Version 3 (Joint Optimization \& Uniform Bounds)}
\author{세라비 \& 세라피}
\date{}

\begin{document}
\maketitle

\section{V3 Overview}
Version 3 aims to \emph{simultaneously} control the off-diagonal term and flip the diagonal--main piece negative under a unified choice of coefficients.

\section{Quadratic Objective}
We define the objective
\begin{equation}
\mathcal{J}_\lambda(c)=2\pi(1-2c^\top s_1+c^\top Kc)+\lambda\,c^\top(B^\top W B)c+\rho\|c\|^2,
\end{equation}
which is convex in $c$. The minimizer is explicit:
\begin{equation}
c^\ast=(2\pi K+\lambda B^\top W B+\rho I)^{-1}(2\pi s_1).
\end{equation}

\section{Acceptance Criteria}
We accept a parameter window if
\begin{equation}
M(c^\ast)\le -\theta\sum|a_n|^2,\qquad
\frac{E_{\mathrm{off}}(c^\ast)}{\sum|a_n|^2}\le \frac{C}{\log N},
\end{equation}
with stable $(\theta,C)$ across $N$.

\section{References}
\begin{thebibliography}{9}

\bibitem{Beurling1955}
A.~Beurling,
\textit{A closure problem related to the Riemann zeta-function},
Proc. Nat. Acad. Sci. U.S.A. 41 (1955), 312--314.

\bibitem{Nyman1950}
B.~Nyman,
\textit{On some groups and semigroups of translations},
PhD thesis, Uppsala University, 1950.

\bibitem{BaezDuarte2003}
L.~Báez-Duarte,
\textit{A strengthening of the Nyman--Beurling criterion for the Riemann Hypothesis},
Rendiconti Lincei, 14 (2003), 5--11.

\bibitem{Titchmarsh1986}
E.~C. Titchmarsh (revised by D. R. Heath-Brown),
\textit{The Theory of the Riemann Zeta-Function},
2nd ed., Oxford University Press, 1986.

\bibitem{Conrey2003}
J.~B. Conrey,
\textit{The Riemann Hypothesis},
Notices Amer. Math. Soc. 50 (2003), 341--353.

\end{thebibliography}

\end{document}
